Optimal Peak Shaving with Bifacial Solar PV: Simulated Storage Battery Dispatch for Electric Vehicle Charging Load

### 2023-12-21 Paper/paper.tex
paper v2 sent to ema

Peak load management, or peak shaving, is the process of reducing the maximum load at a given point in an electrical network. This will necessarily increase the load factor,$P_{load,avg} P_{load,max}^{-1}$, even if load curtailment is the only method used. Other methods include load scheduling, load shifting using energy storage, and reduction of the effective load with distributed generation (DG) \cite{Uddin2018}. Peak shaving may include the concept of a peak load threshold which defines a maximum desired peak load during a period, typically on the order of hours. Grid operators may use peak shaving to increase power quality, defer future infrastructure upgrades, decrease losses, or reduce energy costs. End-users typically reduce their peaks solely on a cost basis. Lastly, some carbon reduction is possible by reducing the on/off transitions of peaker plants due to load peaks \cite{Uddin2018}.

@@

\begin{table}
  \centering
  \caption{Economic and Technical Peak Shaving Comparison}
  \label{tab:econ-tech-peak-shaving}
  \begin{tabularx}{\textwidth}{XXX}
    \toprule
    Feature                                & Technical Peak Shaving                    & Economic Peak Shaving             \\
    \midrule
    Consequence of exceeding the threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
    Time resolution                        & $\mu s$ to 10 s                           & 15-60 min or 1 h (typical)        \\
    Valid times of day                     & All                                       & Limited (e.g. 16:00 to 21:00)     \\
    Peak is recalculated every..           & Continuous (never recalculated)           & Month (also: day, year)        \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

Economic peak shaving aims to reduce what a consumer pays for power and or energy. Medium and large electric consumers often pay an energy price ($p_e\ [\$/kWh]$) and a power price ($p_p\ [\$/kW]$), also called a demand charge. Each may vary with time of day, day of week, and season of the year, which is often referred to as time of use (TOU) or peak pricing. The power cost ($p_p max(P_{load}\ [\$])$) typically applies to the max power during the billing period, where the max power is the maximum non-moving average calculated on a given interval, such as 60 minutes. Where there is a sufficient spread between the peak and off-peak prices there may be the opportunity to load reschedule, shift, or curtail, or dispatch DG.

@@

This work considers a common end-user, economic peak shaving application seen in North America which is described in Equation \ref{eq:peakshaving}. The load may not be curtailed or rescheduled, but solar DG naturally reduces the load and a storage battery is dispatched in a threshold-based peak shaving strategy. The minimum time interval of the threshold is 1 hour.

@@

\begin{equation}
  \label{eq:peakshaving}
  \begin{split}
    P_{threshold,h} & \ge P_{load,h} - P_{solar,h} - P_{batt,discharge,h} + P_{batt,charge,h}                     \\
                    & \text{where:}                                                                               \\
    P               & \text{ is average power (threshold, load, solar, battery) }\ [kW]                           \\
    0               & \le  P_{load,h}, P_{solar,h}, P_{batt,discharge,h}, P_{batt,discharge,h}, P_{batt,charge,h} \\
    h               & \in \{0,1,2,...,23\}                                                                        \\
  \end{split}
\end{equation}

\begin{equation}
  \label{eq:net-load}
  \begin{split}
    NL & = L - S                                                               \\
       & \text{where:}                                                         \\
       & NL(t) \text{ is the net load time series (non-negative)}\ [kW]        \\
       & L(t) \text{ is the EV charging load time series (non-negative)}\ [kW] \\
       & S(t) \text{ is the solar production time series}\ [kW]                \\
  \end{split}
\end{equation}

@@

The main novelty of this work is studying the benefit of vertical bifacial PV modules in a peak shaving application, considering the sensitivity of the solution to percentage of modules facing West and tilted vertical, battery capacity, and overall solar capacity.

@@

\subsubsection{{EV Charging Load }}\label{ev-charging-load}%}

@@

\subsubsection{Solar Production}\label{solar-production}%}

Satellite irradiance data from the Geostationary Operational Environmental Satellite (GOES) is used as the primary data for modeling solar production and is obtained from the US National Solar Resource Database (NSRDB) \cite{Sengupta2018}. The data is serially complete and is available in 2 km by 2 km spatial resolution and 5 minute temporal resolution from 2018 onward. Multi-channel measurements from GOES are fed into the two-step Physical Solar Model (PSM) v3  \cite{Sengupta2018}. In the first step cloud and aerosol properties are collected and passed to the second step where the Fast All-sky Radiation Model for Solar Applications (FARMS), which estimates the radiation transfer on a tilted surface \cite{Xie2016}. Global Horizontal Irradiance (GHI) is computed directly from FARMS, then either REST2 or DISC models are used to compute Diffuse Normal Irradiance (DNI) if the environment is cloudy or clear, respectively \cite{Xie2018}. Authors indicate that computing surface irradiance in cloudy environments is complicated due to absorption and scattering within clouds, which may be a source of error relative to true measured solar PV production. Note these data are not organized into Typical meteorological Year (TMY) but are true satellite measurements for the same day and location as the EV charging load data.

@@

\begin{equation}
  \label{eq:cost}
  \begin{split}
    C_m & = \Sigma_k^K [ p_{p,k,m} max(NL^+_{k,m} + B_d - B_c + p_{e,k,m} \Sigma (NL^+_{k,m} + B_d(t) - B_c(t)) ] \\
        & \text{where:}                                                                                           \\
        & NL^+(t) = NL(t),\ \forall\ NL(t)>0                                                                      \\
        & B_c(t) \text{ is battery charging power time series(non-negative)}\ [kW]                                \\
        & B_d(t) \text{ is battery discharging power time series(non-negative)}\ [kW]                             \\
        & C_m \text{ is total retail electric cost for month}\ m\ [\$]                                            \\
        & p_{p,k,m} \text{ is power price for TOU period}\ k\ \text{and month}\ m\  [\$/kW]                       \\
        & p_{e,k,m} \text{ is energy price for TOU period}\ k\ \text{and month}\ m\ [\$/kWh]                      \\
        & K \text{ is number of TOU periods}
  \end{split}
\end{equation}

Since the problem in question is economic peak shaving, the retail tariff is an important study parameter because it shapes the cost function and determines the benefit of solar production shifted into the late afternoon. With non-zero power prices a threshold-based peak shaving approach is appropriate because it mimics the power component of the true cost function, which concerns the maximum value and not every individual power value. Once the threshold is met, the optimizer knows that "power is free" and will charge the battery up the threshold without penalty to the cost function. Energy of course is paid by the integral of power and therefore any marginal consumption results in a marginal cost.

@@

\begin{figure}
  \centering
  \includegraphics[width=7.5cm]{./images/peak shaving flowchart.png}
  \caption{Peak Shaving Flowchart. Net load is the time series of load less solar. There is one threshold value for one for each TOU period with a non-zero power price. For each timestep of the simulation the net load is compared to the threshold of the current TOU period. The battery is discharged if the net load is greater than the threshold and charged if the net load is less than the threshold. If the two are equal or if there is no power price the battery does nothing.}
  \label{fig:peakshaving-flowchart}
\end{figure}

@@

\begin{equation}
  \label{eq:optimization}
  \begin{split}
    min[C_m(B_c,B_d)] & = min[C_m(T_1,T_2,..T_K)]                                                    \\
                      & s.t.                                                                         \\
    B_c(t)            & \le B_{c,max}                                                                \\
    B_d(t)            & \le B_{d,max}                                                                \\
    SOC_{min}         & \le SOC \le SOC_{max}                                                        \\
                      & \text{where:}                                                                \\
    T_k               & \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
    SOC(t)            & \text{ is battery state of charge timeseries}\ [\frac{kWh}{kWh}]             \\
  \end{split}
\end{equation}

@@

All case studies use the same electric load and tariff, and solar production changes for each case.

The load is measured EV charging power ("load") from the Caltech Adaptive Charging Network database at the Jet Propulsion Lab (JPL) site \cite{Lee2021}. The time series data interval is 10 s, and the data period is from 2018-5-1 00:00 to 2019-2-28 23:45. See Table \ref{tab:data-summary}.

@@

The electric tariff is typical for California and consists of several different TOU periods, summarized in Table \ref{tab:tariff}. Each TOU period may have an energy price (\(\$/kWh\)), a power price (\(\$/kW\)), or both. Some prices change seasonally as well.

\begin{table}[!h]
  \centering
  \caption{Retail Electric Tariff. An applicable electric tariff schedule with power and energy prices for several different TOU periods. From California PG\&E.}
  \label{tab:tariff}
  \begin{tabularx}{\textwidth}{XXXXX}
    \toprule
    Name            & TOU Period                         & Summer (Jun 1 - Sept 30) $[\$]$ & Winter (Oct 1 -Feb 28) $[\$]$ & Spring (Mar 1 - May 30) $[\$]$ \\
    \midrule
    All hours       & 0:00-0:00                          & 26.07/$kW$                      & 26.07/$kW$                    & 26.07/$kW$                     \\
    Super off-peak  & 9:00-14:00                         & -\/-                            & -\/-                          & 0.079/$kWh$                    \\
    Off-peak spring & 0:00-9:00, 14:00-16:00, 21:00-0:00 & -\/-                            & -\/-                          & 0.132/$kWh$                    \\
    Off-peak winter & 0:00-16:00, 21:00-0:00             & -\/-                            & 0.132/$kWh$                   & -\/-                           \\
    Off-peak summer & 0:00-14:00, 23:00-0:00             & 0.132/$kWh$                     & -\/-                          & -\/-                           \\
    Partial-peak    & 14:00-16:00, 21:00-23:00           & 6.81/$kW$, 0.159/$kWh$          & -\/-                          & -\/-                           \\
    Peak            & 16:00-21:00                        & 32.90/$kW$, 0.196/$kWh$         & 2.22/$kW$, 0.172/$kWh$        & 2.22/$kW$, 0.172/$kWh$         \\
    \bottomrule
  \end{tabularx}
\end{table}

Different solar array orientations are modeled and simulated in different case studies, summarized in Table \ref{tab:casestudies}. Each orientation has the same number and type of bifacial modules.

The production time series for all cases is modeled in SAM from GOES satellite irradiance, with one Enphase IQH 380 W microinverter per Prism 350 W bifacial solar PV module, for 368 microinverters and 368 PV modules total. For irradiance data see Table \ref{tab:data-summary}.

The base case is a typical South-facing array tilted at 20˚, called South 20˚ in Table \ref{tab:casestudies}. This is intended to be a compromise rooftop solar design, not achieving the high tilt angles suggested in the literature such as in \cite{Baghoolizadeh2022}, but not as low tilt as common commercial solar arrays especially in northern latitudes where lower sun angles and winter snow make the research question of vertical bifacial modules even more relevant. The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon. The array is sized such that the total energy produced is equal to the total energy consumption of the EV charging station. This "net zero" sizing is not necessarily economically optimal, but rather it is a reasonable assumption for a solar capacity given the load.

The remaining four case studies each consider a percentage of the array permanently rotated West and tilted 90°: 25\%, 50\%, 75\%, and 100\%. The last case is extreme from a design perspective but should be investigated since it represents a maximum amount that midday power can be time-shifted into the late afternoon and evening without tracking or storage. The resulting M-shaped daily power profile is the basis of the advantage vertical bifacial modules may have regarding peak shaving. Microinverters are used in the design so that the cases with a percentage of the array facing West can are indeed a linear combination of the M-shaped and rounded-triangle power profiles.

\begin{table}
  \centering
  \caption{Case Studies. All modules are the Prism 350 W bifacial. The base case is a South-facing array tilted to 20°. In the following four cases, a percentage of the modules are oriented such that the primary high power module surface faces West and the modules are tilted to 90°: 25\%, 50\%, 75\%, and 100\%. As an increasing portion of the array is oriented West and vertical the total energy and solar yield decrease linearly as expected.}
  \label{tab:casestudies}
  \begin{tabularx}{\textwidth}{XXXXXX}
    \toprule
    Case Study                     & Modules & Orientation & Tilt & Total Energy ($MWh$)   & Solar Yield ($\frac{kWh}{kW_{DC}}$) \\
    \midrule
    South 20°                      & 368     & South       & 20°  & 151.7                  & 1180.8                              \\
    \hline
    \multirow{2}{*}{25\% West 90°} & 276     & South       & 20°  & \multirow{2}{*}{146.5} & \multirow{2}{*}{1140.4}             \\
                                   & 92      & West        & 90°  &                        &                                     \\
    \hline
    \multirow{2}{*}{50\% West 90°} & 184     & South       & 20°  & \multirow{2}{*}{141.1} & \multirow{2}{*}{1098.2}             \\
                                   & 184     & West        & 90°  &                        &                                     \\
    \hline
    \multirow{2}{*}{75\% West 90°} & 92      & South       & 20°  & \multirow{2}{*}{136.1} & \multirow{2}{*}{1059.6}             \\
                                   & 276     & West        & 90°  &                        &                                     \\
    \hline
    100\% West 90°                 & 368     & West        & 90°  & 131.0                  & 1019.3                              \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=6.8cm]{./images/total cost.png}
  \includegraphics[width=6.8cm]{./images/total cost reduction.png}
  \caption{Total Retail Electric Cost. Costs are calculated for each case study and a sensitivity analysis is performed on battery capacity (kWh). Below 150 kW the South 20° and 100\% West 90° arrays have similarly high total costs, whereas the three combination arrays are somewhat grouped a few percent below. Above 150 kW the total costs for each case diverge somewhat, with the South 20° base case attaining the lowest cost for the 400 kWh battery and larger. RIGHT: Reduction in Total Retail Cost is likely the most important metric for evaluating the peak shaving efficacy since it can be directly used as revenue in a cash flow analysis to calculate economic performance. The combination of the 50\% West 90° array and 100 kWh battery achieved the largest cost reduction of \$1422 (6.7\%) over the 10-month data period. A selection of the data generating these graphs is shown in Table \ref{tab:data-summary}.}
  \label{fig:total-cost}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\textwidth]{./images/single day of peak shaving.png}
  %\includegraphics[width=6.8cm]{./images/single day of peak shaving south.png}
  %\includegraphics[width=6.8cm]{./images/single day of peak shaving west.png}
  \caption{Single Day of Simulated Peak Shaving (Stacked Dispatch). Solid lines are load: EV charging load (magenta) and additional storage battery charging load (blue). Solid areas are energy sources and always sum up to a solid line unless solar production is greater than the load and is exported to the grid. The TOU power thresholds are represented by the dashed line segments. The dash-dot line is SOE, referenced to the right vertical axis. LEFT: The base South 20° solar array overproduces midday and exports energy to the grid. RIGHT: The 100\% West 90° case exports less solar to the grid, and has more late afternoon production aligned with the evening load peak, allowing the peak shaving algorithm to achieve a 42\% lower Peak period threshold of 7.7 kW than the South 20° array.}
  \label{fig:peak-shaving}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=10cm]{./images/total cost reduction solar sensitivity.png}
  \caption{Solar Capacity Sensitivity. A sensitivity analysis on solar capacity shows more available cost reduction, which increases less than linearly with solar capacity.}
  \label{fig:solar-sensitivity}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=10cm]{./images/bifacial_peak_shaving_paper.assets/weekly load solar.png}
  \caption{Weekly Overlaid Load and Solar Power. The entire 10-month time series of EV charging load, Solar 20°, and 100\% West 90° are superimposed on a weekly basis, beginning on Monday. The 100\% West 90° case provides a clearer graphical example than the better-performing cases.}
  \label{fig:weekly-load-solar}
\end{figure}

>>>>

Peak load management, or peak shaving, is the process of reducing the maximum load at a given point in an electrical network. This will necessarily increase the load factor ($P_{load,avg} P_{load,max}^{-1}$) even if load curtailment is the only method used. Other methods include load scheduling, load shifting using energy storage, and reduction of the effective load with distributed generation (DG) \cite{Uddin2018}. Peak shaving may include the concept of a peak load threshold which defines a maximum desired peak load during a period, typically on the order of hours. Grid operators may use peak shaving to increase power quality, defer future infrastructure upgrades, decrease losses, or reduce energy costs. End-users typically reduce their peaks solely on a cost basis. Lastly, some carbon reduction is possible by reducing the on/off transitions of peaker plants due to load peaks \cite{Uddin2018}.

@@

\begin{table}
  \centering
  \caption{Economic and Technical Peak Shaving Comparison}
  \label{tab:econ-tech-peak-shaving}
  \begin{tabularx}{\linewidth}{X X X}
    \toprule
    Feature                                & Technical Peak Shaving                    & Economic Peak Shaving             \\
    \midrule
    Consequence of exceeding the threshold & Damage to infrastructure, possible outage & Monetary cost depending on tariff \\
    Time resolution                        & $\mu s$ to 10 s                           & 15-60 min (typical)        \\
    Valid times of day                     & All                                       & Limited (e.g. 16:00 to 21:00)     \\
    Peak is recalculated every..           & Continuous (never recalculated)           & Month (also: day, year)        \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

Economic peak shaving aims to reduce what a consumer pays for power and or energy. Medium and large electric consumers often pay an energy price ($p_e\ [\$/kWh]$) and a power price ($p_p\ [\$/kW]$), also called a demand charge. Each may vary with time of day, day of week, and season of the year, which is often referred to as time of use (TOU) or peak pricing. The power cost ($p_p P_{load,max}\ [\$]$) typically applies to the max power during the billing period, where the max power is the maximum non-moving average calculated on a given interval, such as 60 minutes. Where there is a sufficient spread between the peak and off-peak prices there may be the opportunity to reschedule, shift, or curtail load, or dispatch DG.

@@

This work considers a common end-user, economic peak shaving application seen in North America which is described in Equation \ref{eq:net-load}. The load may not be curtailed or rescheduled, but solar DG naturally reduces the load and a storage battery is dispatched in a threshold-based peak shaving strategy. The minimum time interval of the threshold is 1 hour.

@@

\begin{equation}
  \label{eq:net-load}
  \begin{split}
    & \text{Given:} \\
    NL & = L - S                                                               \\
    SL & = NL - B_d + B_c                                 \\
    & \exists B_d, B_c \text{ s.t. } T \ge SL \forall t \\
       & \text{where:}                                                         \\
       NL(t) & \in \mathbb{R} [kW] \text{ is the net load time series }         \\
       L(t) & \in \mathbb{R}^+ [kW] \text{ is the EV charging load time series } \\
       S(t) &\in \mathbb{R}^+ [kW] \text{ is the solar production time series }                \\
       SL(t) & \in \mathbb{R} [kW] \text{ is the site load time series seen at the electric meter }         \\
       B_c(t) & \in \mathbb{R}^+ [kW] \text{ is the battery charging load time series }  \\
       B_d(t) &\in \mathbb{R}^+ [kW] \text{ is the battery discharge time series }   \\
       T(t) &\in \mathbb{R}^+ [kW] \text{ is power threshold }   \\
  \end{split}
\end{equation}

@@

The main novelty of this work is studying the benefit of vertical bifacial PV modules in a peak shaving application, considering the sensitivity of the solution to a percentage of modules facing West and tilted vertically, battery capacity, and overall solar capacity.

@@

%\subsubsection{{EV Charging Load }}\label{ev-charging-load}%}

@@

%\subsubsection{Solar Production}\label{solar-production}%}

Satellite irradiance data from the Geostationary Operational Environmental Satellite (GOES) is used as the primary data for modeling solar production and is obtained from the US National Solar Resource Database (NSRDB) \cite{Sengupta2018}. The data is serially complete and is available in 2 km by 2 km spatial resolution and 5-minute temporal resolution from 2018 onward. Multi-channel measurements from GOES are fed into the two-step Physical Solar Model (PSM) v3  \cite{Sengupta2018}. In the first step cloud and aerosol properties are collected and passed to the second step where the Fast All-sky Radiation Model for Solar Applications (FARMS), which estimates the radiation transfer on a tilted surface \cite{Xie2016}. Global Horizontal Irradiance (GHI) is computed directly from FARMS, then either REST2 or DISC models are used to compute Diffuse Normal Irradiance (DNI) if the environment is cloudy or clear, respectively \cite{Xie2018}. Authors indicate that computing surface irradiance in cloudy environments is complicated due to absorption and scattering within clouds, which may be a source of error relative to true measured solar PV production. Note these data are not organized into Typical meteorological Year (TMY) but are true satellite measurements for the same day and location as the EV charging load data.

@@

\begin{equation}
  \label{eq:cost}
  \begin{split}
    C_m & = \sum_k^K [p_{p,k,m}  max(SL^+_{k,m})] + \sum_k^K [p_{e,k,m} \sum (SL^+_{k,m}) ] \\
        & \text{where:}                                                                                           \\
        SL_{k,m}^+(t) &= SL(t) \forall SL(t)>0 \text{ in TOU period $k$ and month $m$} \\
        C_m & \in \mathbb{R}^+ [\$] \text{ is total retail electric cost for month}\ m\                                             \\
        p_{p,k,m} & \in \mathbb{R}^+ [\$/kW] \text{ is power price for TOU period}\ k\ \text{and month}\ m\                         \\
        p_{e,k,m} & \in \mathbb{R}^+ [\$/kWh] \text{ is energy price for TOU period}\ k\ \text{and month}\ m\                       \\
        K & \in \mathbb{Z}^+ \text{ is the number of TOU periods}
  \end{split}
\end{equation}

Since the problem in question is economic peak shaving, the retail tariff is an important study parameter because it shapes the cost function and determines the benefit of solar production shifted into the late afternoon. With non-zero power prices, a threshold-based peak shaving approach is appropriate because it mimics the power component of the true cost function, which concerns the maximum value and not every individual power value. Once the threshold is met, the optimizer knows that "power is free" and will charge the battery up the threshold without penalty to the cost function. Energy of course is paid by the integral of power and therefore any marginal consumption results in a marginal cost.

@@

\begin{figure}
  \centering
  \includegraphics[width=7.5cm]{./images/peak shaving flowchart.png}
  \caption{Peak Shaving Flowchart. Net load is the time series of load with solar subtracted. There is one threshold value for one for each TOU period with a non-zero power price. For each timestep of the simulation, the net load is compared to the threshold of the current TOU period. The battery is discharged if the net load is greater than the threshold and charged if the net load is less than the threshold. If the two are equal or if there is no power price the battery does nothing.}
  \label{fig:peakshaving-flowchart}
\end{figure}

@@

\begin{equation}
  \label{eq:optimization}
  \begin{split}
    min[C_m(B_c,B_d)] & = min[C_m(T_1,T_2,..T_K)]                                                    \\
                      & s.t.                                                                         \\
    B_c(t)            & \le B_{c,max}                                                                \\
    B_d(t)            & \le B_{d,max}                                                                \\
    SOC_{min}         & \le SOC \le SOC_{max}                                                        \\
                      & \text{where:}                                                                \\
    T_k               & \in \mathbb{R}^+ [kW] \text{ is threshold for}\ k\text{-th TOU period of}\ K\ \text{total periods} \\
    SOC(t)            & \in \mathbb{R}^+ \le 1 [kWh/kWh]  \text{ is battery state of charge timeseries}\             \\
  \end{split}
\end{equation}

@@

All case studies use the same electric load and tariff, and solar production changes for each case. The load is measured EV charging power ("load") from the Caltech Adaptive Charging Network database at the Jet Propulsion Lab (JPL) site \cite{Lee2021}. The time series data interval is 10 s, and the data period is from 2018-5-1 00:00 to 2019-2-28 23:45. See Table \ref{tab:data-summary}. The electric tariff is typical for California and consists of several different TOU periods, summarized in Table \ref{tab:tariff}. Each TOU period may have an energy price (\(\$/kWh\)), a power price (\(\$/kW\)), or both. Some prices change seasonally as well.

% The two largest power prices are 26.07 $\$/kW$ associated with the "All hours" period for all seasons and 32.90 $\$/kW$ associated with the "Peak (Summer)" period of 16:00-21:00, when the vertical West-facing bifacial modules will produce more energy in the late afternoon and evening than the South-facing modules. Since load curtailment is not considered, the battery will only have the option to shift energy from the expensive Peak period to other periods. Since all other periods have the 26.07 $\$/kW$ price, the marginal power cost reduction for shifting 1 kW of peak load out of the Peak period is only \$32.90.

@@

\begin{table}[!h]
  \centering
  \caption{Retail Electric Tariff. An applicable electric tariff schedule with power and energy prices for several different TOU periods. From California PG\&E.}
  \label{tab:tariff}
  \begin{tabularx}{\textwidth}{XXXXX}
    \toprule
    Name            & TOU Period                         & Summer (Jun 1 - Sept 30) $[\$]$ & Winter (Oct 1 -Feb 28) $[\$]$ & Spring (Mar 1 - May 30) $[\$]$ \\
    \midrule
    All hours       & 0:00-0:00     3                     & 26.07/$kW$                      & 26.07/$kW$                    & 26.07/$kW$                     \\
    Super off-peak  & 9:00-14:00                         & -\/-                            & -\/-                          & 0.079/$kWh$                    \\
    Off-peak spring & 0:00-9:00, 14:00-16:00, 21:00-0:00 & -\/-                            & -\/-                          & 0.132/$kWh$                    \\
    Off-peak winter & 0:00-16:00, 21:00-0:00             & -\/-                            & 0.132/$kWh$                   & -\/-                           \\
    Off-peak summer & 0:00-14:00, 23:00-0:00             & 0.132/$kWh$                     & -\/-                          & -\/-                           \\
    Partial-peak    & 14:00-16:00, 21:00-23:00           & 6.81/$kW$, 0.159/$kWh$          & -\/-                          & -\/-                           \\
    Peak            & 16:00-21:00                        & 32.90/$kW$, 0.196/$kWh$         & 2.22/$kW$, 0.172/$kWh$        & 2.22/$kW$, 0.172/$kWh$         \\
    \bottomrule
  \end{tabularx}
\end{table}

The five case studies in Table \ref{tab:casestudies} consider different solar orientations, each with an increasing percentage of the modules oriented West and tilted vertically. The solar production time series for all cases is modeled in SAM from GOES satellite irradiance (Table \ref{tab:data-summary}), with one Enphase IQH 380 W microinverter per Prism 350 W bifacial solar PV module, for 368 microinverters and 368 PV modules total.

The base case is a typical South-facing array tilted at 20˚, called South 20˚ in Table \ref{tab:casestudies}. This is intended to be a compromise between the high tilt angles suggested in \cite{Baghoolizadeh2022} and the low rooftop tilt angles preferred by in industry for the higher coverage ratio and lower wind load \cite{Cao2013}. The daily clear sky solar power profile is the familiar rounded triangle centered at solar noon, such as in Figure \ref{fig:weekly-load-solar}. The array is sized such that the total energy produced is equal to the total energy consumption of the EV charging station. This "net zero" sizing is not necessarily economically optimal, but rather it is a reasonable assumption for a solar capacity given the load.

The remaining four case studies in Table \ref{tab:casestudies} consider a percentage of the array permanently rotated West and tilted 90°: 25\%, 50\%, 75\%, and 100\%. The last case is extreme from a design perspective but should be investigated since it represents a maximum amount that midday production can be time-shifted into the late afternoon and evening without tracking or storage. Graphically that shift results from the M-shaped daily power profile seen in Figure \ref{fig:weekly-load-solar}. Microinverters are used in the design so that the cases with a percentage of the array facing West can are indeed a linear combination of the M-shaped and rounded-triangle power profiles.

\begin{table}
  \centering
  \caption{Case Studies. All modules are the Prism 350 W bifacial. The base case array faces South and is tilted to 20°. The following four cases orient an increasing percentage of the modules West and tilt to 90°, with an expected linear decrease in total energy and solar yield.}
  \label{tab:casestudies}
  \begin{tabularx}{\textwidth}{XXXXXX}
    \toprule
    Case Study                     & Modules & Orientation & Tilt & Total Energy ($MWh$)   & Solar Yield ($\frac{kWh}{kW_{DC}}$) \\
    \midrule
    South 20° (base)               & 368     & South       & 20°  & 151.7                  & 1180.8                              \\
    \hline
    \multirow{2}{*}{25\% West 90°} & 276     & South       & 20°  & \multirow{2}{*}{146.5} & \multirow{2}{*}{1140.4}             \\
                                   & 92      & West        & 90°  &                        &                                     \\
    \hline
    \multirow{2}{*}{50\% West 90°} & 184     & South       & 20°  & \multirow{2}{*}{141.1} & \multirow{2}{*}{1098.2}             \\
                                   & 184     & West        & 90°  &                        &                                     \\
    \hline
    \multirow{2}{*}{75\% West 90°} & 92      & South       & 20°  & \multirow{2}{*}{136.1} & \multirow{2}{*}{1059.6}             \\
                                   & 276     & West        & 90°  &                        &                                     \\
    \hline
    100\% West 90°                 & 368     & West        & 90°  & 131.0                  & 1019.3                              \\
    \bottomrule
  \end{tabularx}
\end{table}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=0.49\textwidth]{./images/total cost.png}
  \includegraphics[width=0.49\textwidth]{./images/total cost reduction.png}
  \caption{Total Retail Electric Cost. Costs are calculated for each case study and a sensitivity analysis is performed on battery capacity (kWh). Below 150 kW the South 20° and 100\% West 90° arrays have similarly high total costs, whereas the three combination arrays are somewhat grouped a few percent below. Above 150 kW the total costs for each case diverge somewhat, with the South 20° base case attaining the lowest cost for the 400 kWh battery and larger. RIGHT: Reduction in Total Retail Cost is likely the most important metric for evaluating the peak shaving efficacy since it can be directly used as revenue in a cash flow analysis to calculate economic performance. The combination of the 50\% West 90° array and 100 kWh battery achieved the largest cost reduction of \$1422 (6.7\%) over the 10-month data period. A selection of the data generating these graphs is shown in Table \ref{tab:data-summary}.}
  \label{fig:total-cost}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \includegraphics[width=\textwidth]{./images/single day of peak shaving.png}
  %\includegraphics[width=6.8cm]{./images/single day of peak shaving south.png}
  %\includegraphics[width=6.8cm]{./images/single day of peak shaving west.png}
  \caption{Single Day of Simulated Peak Shaving. Solid lines are load from EV charging (magenta) and the additional amount of storage battery charging (blue). Solid areas are energy sources and always sum up to the load unless solar production is greater than the load and is exported to the grid. Dashed line segments are TOU power thresholds. The dash-dot line is SOE, referenced to the right vertical axis. LEFT: The base South 20° solar array overproduces midday and exports energy to the grid. RIGHT: The 100\% West 90° case shifts production to the late afternoon, reducing the evening load energy and thereby the Peak period threshold to 7.7 kW, 42\% lower than the South 20° array.}
  \label{fig:peak-shaving}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=12cm]{./images/total cost reduction solar sensitivity.png}
  \caption{Solar Capacity Sensitivity. A sensitivity analysis on solar capacity shows more available cost reduction, which increases less than linearly with solar capacity.}
  \label{fig:solar-sensitivity}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{./images/weekly load solar.png}
  \caption{Weekly Overlaid Load and Solar Power. The entire 10-month time series of EV charging load, Solar 20°, and 100\% West 90° are superimposed on a weekly basis, beginning on Monday. The 100\% West 90° case provides a clearer graphical example than the better-performing cases.}
  \label{fig:weekly-load-solar}
\end{figure}
